
\section*{Problem 3}

Between the network layer and the link layer there is a packet scheduler in which one can implement dif-ferent queuing disciplines (qdisc).
The standard one is called pfifo which stands for packet-first-in-first-out.There are also other queuing disciplines such as Codel (Control Delay) and sfq (Stochastic Fair Queueing).
In this problem we will study an application based qdisc.

We assume that the SSH application generates low volume of packets (which is typically the case froma SSH client to the SSH server).
We assume that the FTP application generates high volume of packets.

This would be the case if the end-system is uploading a large file.
Packets arrivals follow a Poisson processwith average arrival rates $\lambda_{\text{SSH}}$, $\lambda_{\text{FTP}}$ packets per second for SSH and FTP, respectively.
Assume that theSSH and FTP packet arrival processes are independent.

We will consider two scheduling discipline

\begin{enumerate}
    \item Timer based:  SSH packets wait until the timer expires, at which time the FTP packets are buffered and all SSH packets are serviced.
          We refer to each timer expiry as a ``dump'' and assume that a dumptakes zero time (i.e., all SSH packets are sent instantly for link level processing).
          The time between dumps is denoted by $T$ seconds.
    \item Number based: SSH packets wait until a certain number of them have accumulated at which time the FTP packets are buffered and all SSH packets are serviced.
          The number of packet to accumulate fora dump is denoted by $N$.
\end{enumerate}

For the above disciplines answer the following

\begin{enumerate}
    \item For the timer based scheduling what is the expected number of SSH packets that are forwarded forlink layer processing on any dump.
    \item For the timer based scheduling what is the probability that zero SSH packets are forwarded on anyparticular dump.
    \item For the number based scheduling what is the expected number of SSH packets that are forwarded forlink layer processing on any dump.
    \item For the number based scheduling what is the expected time that a randomly arriving SSH packet mustwait until service.
\end{enumerate}
\subsection*{Solution}

\begin{enumerate}
    \item $T \lambda_{\text{SSH}}$
    \item $P(k = 0) = \frac{(T \lambda_{\text{SSH}})^k e^{-T \lambda_{\text{SSH}}}}{k!} = e^{-T \lambda_{\text{SSH}}}$
    \item $N$
    \item
\end{enumerate}