
\section*{Problem 6}

Read the paper titled ``Congestion Avoidance and Control'' and write a short 300 word summary.

\subsection*{Solution}

The paper focuses on congestion avoidance.
In the introduction, the authors first established that congestion appears when equilibrium can't be reaches.
Then they identified the reason for it.

\begin{enumerate}
    \item The connection doesn’t get to equilibrium, or
    \item A sender injects a new packet before an old packet has exited, or
    \item The equilibrium can’t be reached because of resource limits along the path.
\end{enumerate}

First they analysised slow start.
By keep doubling the packets to send, the equilibrium is reached such that there are enough input packets.
They made sure that problem (1) is solved, the connection always gets to equilibrium.

Then they address problem (2).
When assuming the implementation correctness, (2) means the timer failure.
This can happen when the variance of the RTT is not taken into consideration.
Thus they proposed a estimator via low pass filter:

$$ R = \alpha R + (1-\alpha)M $$

Where $M$ is last RTT measurement, $\alpha = 0.9$.
Then the retransmit timeout is set to $\beta R$.
This can still cause problems, for example, when a packet is retransmitted twice, how should we adapt the timeout?
The author suggests that since the network acts like a linear system, and linear systems stability is exponential, we can add  exponential damping to the network.

Finally, they address problem (3).
First, resource limitations can be 1) packet damaged, or 2) packet dropped due to congestion.
The authors recognized that 1) is less likely (<1\%) when 2) is more common case.
However, the problem is that the network needs a signal to endpoints that congestion just happened.
Based on (1) and (2) being solved, they proposed that timeout can be a pretty good signal.

Suppose $L_i$ is the load at interval $i$, $N$ is average arrival rate, we have

$$L_i = N + \gamma L_{i-1}$$

When there is a congestion, $\gamma$ must be high, then we should multiplicative decrease window size to reduce the packets sent.
When there is no congestion, $\gamma$ can be zero.
However, it would be a mistake to multiplicative increase the window size, instead, we whould only linear increase, given that the increased amount is less than the max window size.

In the end, the authors examined the work that should be done on the gateway side.
Since congestion grows exponentially, detecting it early is important.
The gateways should send the signal that there may be a congestion as soon as possible.
